---
title: "Homework 1"
output: html_notebook
---

Complete the following exercises by Friday, January 13 at 11:59 p.m. Please submit the assignment on GitHub.

## Your Name

## Loading packages

1.  Load the `tidyverse` in the code chunk below.

```{r}
# SOLUTION:
```

* * *

## Manipulating vectors

The `letters` vector is a vector of all lowercase letters of the alphabet.

2.  Determine the length of the `letters` vector.

```{r}
# SOLUTION:
```


3.  Select the 13th letter of the alphabet.

```{r}
# SOLUTION:
```


4.  Select the 17th through 21st letters of the alphabet.

```{r}
# SOLUTION:
```


* * * 

## Applying functions to vectors

Define the vector `x` to have values 3.2,  9.1,  4.3,  3.6,  8.9 (in that order).


5.  Create the vector `x`.

```{r}
# SOLUTION:
```


6. Run the command `floor(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


7. Run the command `celing(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


8.  Run the command `round(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


9.  Run the command `abs(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


10. Run the command `min(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


11. Run the command `max(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


12. Run that command `which.min(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


13. Run the command `which.max(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```
